|

### 2023-04-04 appendix.Rmd
Modify the scale for the p-value cmp plot.
 Also draw an area for adj. p-value < 0.05

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line is to indicate $p\\text{-value} = 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$."}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  mutate(diff_p_value = adjusted_p_value - p_value) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0.05, col = "red", linetype = 2) +
  geom_point(aes(p_value, diff_p_value), alpha = 0.2) +
  scale_x_log10() +
  facet_wrap(~modified) +
  ylab(expression("Adjusted"~italic(p)*"-value minus"~italic(p)*"-value")) +
  xlab(expression(italic(p)*"-value")) +
  theme_light()

```

>>>>

```{r sensitivity, fig.cap = "Change of $p$-values with $\\hat{\\alpha}$ multiplied by $0.5$, $0.75$, $0.875$, $1.125$, $1.25$ and $1.5$. The vertical dashed line indicates $p\\text{-value} = 0.05$. The area coloured in red indicates $\\text{adjusted }p\\text{-value} < 0.05$. The x-axis is drawn on logarithmic scale. For multiplier smaller than $1$, the adjusted $p$-value will incrase then decrase as $p$-value increases. The trend is the opposite for multiplier greater than $1$, but the difference will eventually reach $0$."}

smallest_p_value <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  pull(p_value) %>%
  min()

upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  mutate(diff_p_value = adjusted_p_value - p_value) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0.05, col = "black", linetype = 2, alpha = 0.7) +
  geom_ribbon(data = expand.grid(x = 10^seq(-10, 0, 0.01),
                                y = seq(-0.1, 0.1, 0.0001)) %>%
              filter(x + y < 0.05) %>%
              group_by(x) %>%
              summarise(y = max(y)),
            aes(x, ymax = y, ymin = -0.06),
            fill = "red",
            alpha = 0.2) +
  annotate("text", 
           x = 0.0005, 
           y = -0.03, 
           label = '"Adjusted"~italic(p)*"-value"~"< 5%"', 
           parse = TRUE,
           col = "red") +
  geom_point(aes(p_value, diff_p_value), alpha = 0.2) +
  facet_wrap(~modified) +
  ylab(expression("Adjusted"~italic(p)*"-value minus"~italic(p)*"-value")) +
  xlab(expression(italic(p)*"-value")) +
  theme_light() +
  scale_x_continuous(breaks = c(0.0001, 0.001, 0.01, 0.1, 1),
                     minor_breaks = NULL,
                     trans = "log10",
                     labels = c("0.01%", "0.1%", "1%", "10%", "100%"),
                     limits = c(smallest_p_value, 1)) +
  scale_y_continuous(limits = c(-0.06, 0.06))
```
